Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-09-15 fib2.tex
whack whack

The defining feature of an Abelian anyon theory
is that the state is completely determined once
we measure the charge of each hole.
In the language of the toric code (homology),
logical operators (1-chains)
cancel where they overlap
with opposite orientation:
\begin{center}
\includegraphics[width=0.7\columnwidth]{pic-abelian.pdf}

\end{center}

@@

@@

We use curve diagrams...
Combinatorial formulation...

>>>>

The defining feature of an Abelian anyon theory
is that the state is completely determined once
we measure the charge of each hole.
In the language of the toric code (homology),
logical operators (1-chains)
cancel where they overlap
with opposite orientation:
\begin{center}
\includegraphics[width=0.7\columnwidth]{pic-abelian.pdf}
\end{center}

@@

Given a disc with $n$ holes, we define the \emph{mapping
class group} $MCG(D_n)$ as the group of topological
symmetries (homeomorphisms) of the space $D_n,$
modulo continuous deformations (isotopy).
Such symmetries we require to fix the boundary
of the disc, but not necessarily to fix the holes.
Elements $f\in MCG(D_n)$ will also act on anything that
resides in $D_n.$ 
In particular, if we draw a line
connecting the holes:
\begin{center}
\includegraphics[]{pic-twist.pdf}
\end{center}

Such an embedding $c : [0, 1] \to D$ with $c(0), c(1) \in \partial D$
and touching all holes in $D_n$ we call a \emph{curve diagram}~\cite{Dehornoy2002}.

\begin{center}
\includegraphics[]{pic-interaction.pdf}
\end{center}

@@

Combinatorial formulation...
